---
title: "Searching through some R Datasets"
output:
  html_document:
    df_print: paged
---

Find data with desired specifics from the next list of datasets. 

http://vincentarelbundock.github.io/Rdatasets/datasets.html

```{r}
library(dplyr)
library(tidyverse)
library(XML)

url <- "http://vincentarelbundock.github.io/Rdatasets/datasets.html"

data_df <- readHTMLTable(url, header = TRUE) # reading the web page

rdatasets <- data_df[[2]] # getting the data frame of datas 

# when reading the data column names have some unnecessary blank space 
# removing blank space
colnames(rdatasets) <- trimws(colnames(rdatasets))

head(rdatasets)
```


```{r}
rdatasets$Rows <- as.numeric(as.character(rdatasets$Rows))
rdatasets$Cols <- as.numeric(as.character(rdatasets$Cols))

# Some neccessary changes, since data "InfantMortality" and "LeafHoppers" don't exist anymore
# Now we have "InfantMortality2010" which has 10 rows and 2 variables and 
# title "Infant Mortality Rates"
# and "Leafhoppers" with 8 rows and 3 columns and 
# title ""
rdatasets$Item <- as.character(rdatasets$Item)
rdatasets$Item[1076] <- "InfantMortality2010"     # "InfantMortality" is in the 1076 row
rdatasets$Item[1080] <- "Leafhoppers"             # "Leafhoopers" i in the 1080 row

rdatasets$Title <- as.character(rdatasets$Title)
rdatasets$Title[1076] <- "Infant Mortality Rates"
rdatasets$Title[1080] <- "Leafhopper Diet and Longevity"   

rdatasets$Rows[1076] <- 10
rdatasets$Cols[1080] <- 3

```

### Install and load packages (Optional)

This is done for easy look at many datasets, and avoiding manualy installing and loading necessary packages

```{r}
# getting the names of unique packages
rdatasets$Package %>% unique() -> pkgs

pkgs <- as.vector(t(pkgs)) # vector of all unique packages 

#install.packages("easypackages")
library(easypackages)


installed_pkgs <- as.data.frame(installed.packages()) # data frame with all installed packages and 
                                                     # some additional information about packages 
head(installed_pkgs$Package) # preview of a first few installed packages' names


# Installing packages that aren't already installed 
t_f <- pkgs %in% installed_pkgs$Package # logical vector to see which packages are already installed

# sum(t_f) = length(pkgs) means that all packages are already installed
if (sum(t_f) != length(pkgs)) install.packages(pkgs[!t_f]) # install packages that aren't already installed

# Loading packages
loaded_pkgs <- (.packages()) # list of already loaded packages

# loading packages that aren't already loaded 
suppressPackageStartupMessages(easypackages::libraries(pkgs[!(pkgs %in% loaded_pkgs)]))  
```

Now you can easily check any data with help().

```{r}
# e.g.
help("dogs")
```

Or you can search through for a specific number of rows, columns, etc.

```{r}
# e.g. 
rdatasets %>% filter(Rows > 5 & Rows <= 30 & Cols == 3 & has_numeric==TRUE) %>% arrange(desc(Rows))
```







Checking if datas have factor, character variables, etc. 


```{r}

# 17th observation is cd4.nesteed which is a bootstrap, not data
# code can't work for bootstrap, so cd4.nested is removed

rdatasets_new <- rdatasets[c(1:16,18:285,288:1243),] # taking everything exept cd4.nested, Harman23.cor, Harman74.cor

itm <- as.character(rdatasets_new$Item)
package_name <- as.character(rdatasets_new$Package)

n <- nrow(rdatasets_new)

v <- vector()

# As there were some mistakes about specification of the datas from the website
# check again for numeric, factor, logical and character variables

# first asigning all of them to NA, and later on to TRUE/FALSE
rdatasets_new$has_numeric <- NA
rdatasets_new$has_factor <- NA
rdatasets_new$has_character <- NA
rdatasets_new$has_logical <- NA


TF_factor <- vector()
TF_num <- vector()
TF_logic <- vector()
TF_char <- vector()

for (i in 1:n){
  
x <- itm[i]
y <- package_name[i]

data(list = x, package = y)
w <- eval(as.name(x))   
v <- is.data.frame(w)

rm(x)
rm(list = itm[i])
  if(!v) {
    w <- as.data.frame(w)  # if something is not a data frame, make it a data frame, so we can do map()
  } 
  
  # checking if the data has variables of factor type
  TF_factor <- (map(w, is.factor)==TRUE)
  if(sum(TF_factor) == 0) {
    rdatasets_new$has_factor[i] <- FALSE
  } else if (sum(TF_factor) > 0){rdatasets_new$has_factor[i] <- TRUE}
  
  # checking if the data has variables of character type
  TF_char <- (map(w, is.character)==TRUE)
  if(sum(TF_char) == 0) {
    rdatasets_new$has_character[i] <- FALSE
  } else {rdatasets_new$has_character[i] <- TRUE}
  
  # checking if the data has variables of logical type
  TF_logic <- (map(w, is.logical)==TRUE)
  if(sum(TF_logic) == 0) {
    rdatasets_new$has_logical[i] <- FALSE
  } else {rdatasets_new$has_logical[i] <- TRUE}
  
  # checking if the data has variables of numeric type
  TF_num <- (map(w, is.numeric)==TRUE)
  if(sum(TF_num) == 0) {
    rdatasets_new$has_numeric[i] <- FALSE
  } else {rdatasets_new$has_numeric[i] <- TRUE}

  
rm(w) # removing w from environment

}

rdatasets_new <- rdatasets_new[,c(1:9,12)]
```



```{r}
summary(rdatasets_new)
```


On the end export the dataset to .csv file, so it can be used for app. 

```{r}
write.csv(rdatasets_new, file = "Rdatas.csv")
```















